\documentclass[a4paper,12pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}

% Page setup
\geometry{a4paper, margin=1in}

% Title and Author
\title{Data Analysis Proposal}
\author{Joe Collins}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
    This document outlines a proposal for conducting data analysis on [brief description of the data]. The analysis aims to [state the objective or goals of the analysis]. The methodology involves [brief description of the methods and tools to be used]. The findings of this analysis will provide valuable insights into [mention the potential impact or significance].
\end{abstract}

\section{Introduction}

The Spains Hall Estate is leading the field introducing 

Since 2019




\section{Objective}
Clearly state the objectives or goals of the data analysis. What specific questions or problems do you intend to address through this analysis?

\section{Methodology}
Outline the methods and tools you plan to use for the data analysis. This may include statistical methods, programming languages, and any relevant software or packages.

\section{Data Collection}
Describe the source of the data, the variables involved, and any data preprocessing steps that may be necessary.

\section{Analysis Plan}
Detail the steps you will take to analyze the data. This could involve exploratory data analysis, statistical tests, machine learning algorithms, etc.

\section{Timeline}
Provide a tentative timeline for completing the data analysis, including key milestones and deadlines.

\section{Expected Results}
Discuss the potential outcomes and insights you expect to derive from the analysis.

\section{Conclusion}
Summarize the key points of the proposal and restate the importance of the proposed data analysis.

\section*{References}
Include any references or citations to relevant literature, data sources, or tools.

\end{document}
