\documentclass{roles}

\title{Using Image Analysis and Machine Learning\\for Biodiversity Monitoring}
\author{Joe Collins - j.collins@zengenti.com}
\date{14 December 2023}

\begin{document}

\maketitle

\section*{Background}

In 2019, the Spains Hall Estate, Essex, initiated a nature recovery and natural flood management program by introducing beavers, into a fenced enclosure https://www.spainshallestate.co.uk/nfm\_beavers.  Comprehensive monitoring of the hydrology, canopy cover, and botanical species composition has been conducted each year (2019-2023) to assess the impact of beavers within the enclosure.  The data from these surveys is freely available at https://github.com/joejcollins/atlanta-shore.  An additional survey will be conducted in mid summer 2024.

As part of the survey geo referenced images have been taken of ground and canopy cover at each of the survey points https://joejcollins.github.io/atlanta-shore/survey-points.html. The images do not provide sufficient detail to identify individual plants but it is hoped that the images contain sufficient information to predict the plant assemblages or Indicator Values https://en.wikipedia.org/wiki/Indicator_value from features in the images.

The project uses R for statistical analysis and Python for data cleaning and preparation. Some familiarity with Git is needed but training can be given. The team includes the estate manager, two ecologists, a hydrologist and a software engineer, and would welcome input from a data scientist.

\section*{Outcomes}

The project aims to streamline botanical assessments by leveraging image data to predict Indicator Values https://en.wikipedia.org/wiki/Indicator_value and plant assemblages. The goal is to develop an algorithm that can accurately analyse images to provide metrics for canopy and ground cover, thus enabling less experienced individuals or botanists with limited time to assess locations efficiently based solely on gross/course image data.

Additionally, there is a plan to create a mobile application that offers basic metrics for canopy and green ground cover. Moreover, this application will utilise image data to predict Indicator Values for specific locations. Such a tool would serve as a convenient and expedited method for verifying whether predictions align with actual observations on the ground.

\section*{Team}

Whilst the Spains Hall estate is a commercial enterprise,
this is a volunteer lead study
run by a collaborative team consisting of:

\begin{description}
    \item[Sarah Brockless] Ecologist \href{https://www.linkedin.com/in/sarah-brockless-833291a7/}{https://www.linkedin.com/in/sarah-brockless-833291a7/}.
    \item[Joe Collins] Software Engineer \href{https://www.linkedin.com/in/joejcollins/}{https://www.linkedin.com/in/joejcollins/}.
    \item[Mags Cousins] Botanist \href{https://www.researchgate.net/profile/Mags-Cousins}{https://www.researchgate.net/profile/Mags-Cousins}
    \item[David Gasca] Hydrologist \href{https://www.linkedin.com/in/david-gasca-7830537/}{https://www.linkedin.com/in/david-gasca-7830537/}.
\end{description}

The team would welcome input from a data scientist.

\section*{Opportunity Details}

\begin{description}
    \item[Data Availability] This is an open source project and
        the data thus far is available on \href{https://github.com/joejcollins/atlanta-shore}{https://github.com/joejcollins/atlanta-shore}.
    \item[Tools] The project uses both R and Python for data preparation and statistical analysis.
        Some familiarity with Git is needed but training can be given.
    \item[Survey Assistance] There will be an opportunity to assist with the botanical survey
        and data collection on site at the Spains Hall Estate, 20-24 June 2024.
    \item[Contact] For further information contact Joe Collins at \href{mailto:j.collins@zengenti.com}{j.collins@zengenti.com}.
\end{description}

\end{document}
